Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2021-02-23 summary.Rmd
fixed typo

Thus, as $n \to \infty$, the partitioning of $\hat{B}^{(n)}$ results in 
perfect community detection. 
This leads to the Orthogonal Spectral Clustering (OSE) algorithm (Alg. 1).

@@

For each simulation, community labels are drawn from a multinomial 
distribution, the popularity vectors $\{\lambda^{(kl)}\}_K$ are drawn 
from two types of joint distributions depending on whether $k = l$, the edge
probability matrix $P$ is constructed using 
the popularity vectors, and finally an unweighted and undirected adjacency 
matrix $A$ is drawn from $P$. OSE is then used for community detection, 
and this method is compared against SSC \cite{noroozi2019estimation}
\cite{soltanolkotabi2014} and MM \cite{igraph}
\cite{307cbeb9b1be48299388437423d94bf1}. True 
community labels are used with Algorithm 3 to estimate the popularity 
vectors $\{\lambda^{(kl)}\}_K$, and this method is then compared against an
MLE-based estimator described in \citet{noroozi2019estimation} and
\citet{307cbeb9b1be48299388437423d94bf1}.

@@

Fig. \ref{fig:clust_err_k} show that for large $n$, OSE results in 
a misclustering rate of 0. Sparse subspace clustering produces similar results 
for $K > 2$.

```{r clust_err_k, fig.cap = 'IQR of clustering error using OSE (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

Theorem 4 implies that OSE will result in not just in the error rate 
converging to 0 but the error *count* as well.
We explore this in Fig. \ref{fig:clust_err_ct_sim}.

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using OSE (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm * n, ymax = third.q.mm * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

Fig. \ref{fig:clust_err_k_imba} and \ref{fig:clust_err_ct_sim_imba} show 
similar results as in the balanced communities case, with both OSE and 
SSC resulting in no misclustered vertices for a 
sufficiently large sample size. However, Fig. \ref{fig:lambda_est_k_imba} 
suggests that while Algorithm 3 retains $\sqrt{n}$ efficiency, the MLE-based 
plug-in estimator is less efficient for this setup.

```{r clust_err_k_imba, fig.cap = 'IQR of clustering error using OSE (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are imbalanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k-imbalanced.csv')
ssc.df <- readr::read_csv('clustering-ssc-k-imbalanced.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

```{r clust_err_ct_sim_imba, fig.cap = 'IQR of counts of misclustered vertices using OSE (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are imbalanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k-imbalanced.csv')
ssc.df <- readr::read_csv('clustering-ssc-k-imbalanced.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm * n, ymax = third.q.mm * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

In the first real data example, we applied OSE to the Leeds Butterfly 
dataset \cite{Wang_2018} consisting of visual similarity measurements among 832 
butterflies across 10 species. The graph was modified to match the example 
from \citet{noroozi2019estimation}: Only the 4 most frequent species were 
considered, and the similarities were discretized to $\{0, 1\}$ via 
thresholding. Fig. \ref{fig:butterfly} shows a sorted adjacency matrix sorted 
by the resultant clustering.

Comparing against the ground truth species labels, OSE achieves an 
accuracy of 63\% and an adjusted Rand index of 73\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\% using 
sparse subspace clustering on the same dataset.

```{r butterfly, fig.height = 2, fig.width = 2, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by OSE.', cache = FALSE}
plot.A(A, z.hat)
```

@@

In the second example, we applied OSE to the British MPs Twitter 
network \cite{greene2013producing}, the Political Blogs network 
\cite{10.1145/1134271.1134277}, and the DBLP network \cite{NIPS2009_3855} 
\cite{10.1007/978-3-642-15880-3_42}. For this data analysis, we subsetted the 
data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
networks. Our methods underperformed compared to modularity maximization, 
although performance is comparable. In 
addition, OSE's runtime is much lower than that of modularity 
maximization.

```{r}
dplyr::tibble(Network = c('British MPs', 'Political blogs', 'DBLP'),
              Vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `Error (Mod. Max.)` = c(round(1 / 329, 3),
                                      round(61 / 1222, 3),
                                      round(62 / 2203, 3)),
              `Error (SSC)` = round(1 - c(bmp.acc.ssc,
                                          pb.acc.ssc,
                                          dblp.acc.ssc), 3),
              `Error (OSE)` = round(1 - c(bmp.acc, 
                                                  pb.acc,
                                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization,',
                               'sparse subspace clustering, ',
                               'and OSE.'))
```

```{r mp, cache = FALSE, fig.width = 8, fig.height = 2, fig.cap = 'Adjacency matrices of (from left to right) the British MPs, Political Blogs, and DBLP networks after sorting by the clustering outputted by OSE.', fig.dpi = 10}
gridExtra::grid.arrange(plot.A(A.bmp, zhat.bmp),
                        plot.A(A.pb, zhat.pb),
                        plot.A(A.dblp, zhat.dblp),
                        ncol = 3)
```

@@

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by OSE (left). The villages studied here are, from left to right, 12, 31, and 46.', fig.height = 2, fig.width = 8, eval = TRUE}
K <- 2
hh.12 <- readRDS('data/village-hh-12.rds')
hh.31 <- readRDS('data/village-hh-31.rds')
hh.46 <- readRDS('data/village-hh-46.rds')

@@

knitr::kable(dplyr::tibble(
  Method = c('OSE', 'SSC', 'Mod. Max.'),
  `Error (Village 12)` = round(1 - c(hh.acc.12, hh.acc.ssc.12, hh.acc.mm.12), 3),
  `Error (Village 31)` = round(1 - c(hh.acc.31, hh.acc.ssc.31, hh.acc.mm.31), 3),
  `Error (Village 46)` = round(1 - c(hh.acc.46, hh.acc.ssc.46, hh.acc.mm.46), 3)),
  caption = paste('Community detection error rates for identifying',
                  'household religion.'))
```

@@

which is a symmetric $(n_k + n_l) \times (n_k + n_l)$ matrix. It can be shown 
that the eigendecomposition of $M^{(kl)}$ is

>>>>

Thus, as $n \to \infty$, the partitioning of $\hat{B}^{(n)}$ results in 
perfect community detection. 
This leads to the Orthogonal Spectral Clustering (OSC) algorithm (Alg. 1).

@@

For each simulation, community labels are drawn from a multinomial 
distribution, the popularity vectors $\{\lambda^{(kl)}\}_K$ are drawn 
from two types of joint distributions depending on whether $k = l$, the edge
probability matrix $P$ is constructed using 
the popularity vectors, and finally an unweighted and undirected adjacency 
matrix $A$ is drawn from $P$. OSC is then used for community detection, 
and this method is compared against SSC \cite{noroozi2019estimation}
\cite{soltanolkotabi2014} and MM \cite{igraph}
\cite{307cbeb9b1be48299388437423d94bf1}. True 
community labels are used with Algorithm 3 to estimate the popularity 
vectors $\{\lambda^{(kl)}\}_K$, and this method is then compared against an
MLE-based estimator described in \citet{noroozi2019estimation} and
\citet{307cbeb9b1be48299388437423d94bf1}.

@@

Fig. \ref{fig:clust_err_k} show that for large $n$, OSC results in 
a misclustering rate of 0. Sparse subspace clustering produces similar results 
for $K > 2$.

```{r clust_err_k, fig.cap = 'IQR of clustering error using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

Theorem 4 implies that OSC will result in not just in the error rate 
converging to 0 but the error *count* as well.
We explore this in Fig. \ref{fig:clust_err_ct_sim}.

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm * n, ymax = third.q.mm * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

Fig. \ref{fig:clust_err_k_imba} and \ref{fig:clust_err_ct_sim_imba} show 
similar results as in the balanced communities case, with both OSC and 
SSC resulting in no misclustered vertices for a 
sufficiently large sample size. However, Fig. \ref{fig:lambda_est_k_imba} 
suggests that while Algorithm 3 retains $\sqrt{n}$ efficiency, the MLE-based 
plug-in estimator is less efficient for this setup.

```{r clust_err_k_imba, fig.cap = 'IQR of clustering error using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are imbalanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k-imbalanced.csv')
ssc.df <- readr::read_csv('clustering-ssc-k-imbalanced.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

```{r clust_err_ct_sim_imba, fig.cap = 'IQR of counts of misclustered vertices using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are imbalanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k-imbalanced.csv')
ssc.df <- readr::read_csv('clustering-ssc-k-imbalanced.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm * n, ymax = third.q.mm * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

In the first real data example, we applied OSC to the Leeds Butterfly 
dataset \cite{Wang_2018} consisting of visual similarity measurements among 832 
butterflies across 10 species. The graph was modified to match the example 
from \citet{noroozi2019estimation}: Only the 4 most frequent species were 
considered, and the similarities were discretized to $\{0, 1\}$ via 
thresholding. Fig. \ref{fig:butterfly} shows a sorted adjacency matrix sorted 
by the resultant clustering.

Comparing against the ground truth species labels, OSC achieves an 
accuracy of 63\% and an adjusted Rand index of 73\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\% using 
sparse subspace clustering on the same dataset.

```{r butterfly, fig.height = 2, fig.width = 2, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by OSC.', cache = FALSE}
plot.A(A, z.hat)
```

@@

In the second example, we applied OSC to the British MPs Twitter 
network \cite{greene2013producing}, the Political Blogs network 
\cite{10.1145/1134271.1134277}, and the DBLP network \cite{NIPS2009_3855} 
\cite{10.1007/978-3-642-15880-3_42}. For this data analysis, we subsetted the 
data as described by 
\citet{307cbeb9b1be48299388437423d94bf1} for their analysis of the same 
networks. Our methods underperformed compared to modularity maximization, 
although performance is comparable. In 
addition, OSC's runtime is much lower than that of modularity 
maximization.

```{r}
dplyr::tibble(Network = c('British MPs', 'Political blogs', 'DBLP'),
              Vertices = c(nrow(A.bmp), nrow(A.pb), nrow(A.dblp)),
              `Error (Mod. Max.)` = c(round(1 / 329, 3),
                                      round(61 / 1222, 3),
                                      round(62 / 2203, 3)),
              `Error (SSC)` = round(1 - c(bmp.acc.ssc,
                                          pb.acc.ssc,
                                          dblp.acc.ssc), 3),
              `Error (OSC)` = round(1 - c(bmp.acc, 
                                                  pb.acc,
                                                  dblp.acc), 3)) %>% 
  knitr::kable(caption = paste('Community detection error rates', 
                               'for modularity maximization,',
                               'sparse subspace clustering, ',
                               'and OSC.'))
```

```{r mp, cache = FALSE, fig.width = 8, fig.height = 2, fig.cap = 'Adjacency matrices of (from left to right) the British MPs, Political Blogs, and DBLP networks after sorting by the clustering outputted by OSC.', fig.dpi = 10}
gridExtra::grid.arrange(plot.A(A.bmp, zhat.bmp),
                        plot.A(A.pb, zhat.pb),
                        plot.A(A.dblp, zhat.dblp),
                        ncol = 3)
```

@@

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by OSC (left). The villages studied here are, from left to right, 12, 31, and 46.', fig.height = 2, fig.width = 8, eval = TRUE}
K <- 2
hh.12 <- readRDS('data/village-hh-12.rds')
hh.31 <- readRDS('data/village-hh-31.rds')
hh.46 <- readRDS('data/village-hh-46.rds')

@@

knitr::kable(dplyr::tibble(
  Method = c('OSC', 'SSC', 'Mod. Max.'),
  `Error (Village 12)` = round(1 - c(hh.acc.12, hh.acc.ssc.12, hh.acc.mm.12), 3),
  `Error (Village 31)` = round(1 - c(hh.acc.31, hh.acc.ssc.31, hh.acc.mm.31), 3),
  `Error (Village 46)` = round(1 - c(hh.acc.46, hh.acc.ssc.46, hh.acc.mm.46), 3)),
  caption = paste('Community detection error rates for identifying',
                  'household religion.'))
```

@@

which is a symmetric $(n_k + n_l) \times (n_k + n_l)$ matrix. It can be shown 
that the spectral decomposition of $M^{(kl)}$ is
